---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# causalbkmr:  a suite of functions for causal Bayesian Kernel Machine Regression (causal-BKMR)

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/zc2326/causalbkmr.svg?branch=master)](https://travis-ci.com/zc2326/causalbkmr)
<!-- badges: end -->
 

## About the Package 

The R package `causalbkmr` consists of three parts: `BKMR-CMA` for Bayesian Kernel Machine Regression-Causal Mediation Analysis, `MI-BKMR` for Multiple Imputation BKMR, and `g-BKMR` for Bayesian Kernel Machine Regression for time-varying exposures and time-varying confounders. 
 
We welcome your feedback and questions (email zc2326@columbia.edu)!

## Installation 

You can install the latest version of `causalbkmr` via: 

``` r
devtools::install_github("zc2326/causalbkmr")
```

Load `causalbkmr`:

```{r loadpackage}
library(causalbkmr) 
```



### BKMR-CMA

A command that allows the estimation of direct and indirect health effects of multiple environmental exposures through a single mediator. 

Cite the paper: [Bayesian kernel machine regression-causal mediation analysis](https://onlinelibrary.wiley.com/doi/full/10.1002/sim.9255?casa_token=lf0hlEtqtjgAAAAA%3AyPLEllmuJGIeEN9ZMIr7kT33RjXQmjiLbUq4JjqfI5dxlSvkdeVjzkEiOqG9Rbh70Frxe3ONzA2aql8)

See the [Quick Start guide](https://zc2326.github.io/causalbkmr/articles/BKMRCMA_QuickStart.html) for `BKMR-CMA`. See the package [website](https://zc2326.github.io/causalbkmr/articles/BKMRCMA_method_overview.html) for an overview of statistical modeling approaches.

 
### MI-BKMR

A command that is used for valid estimation of environmental mixture effects and evaluation of uncertainty in the presence of missing data, which are imputed using multiple imputation techniques. The commands also produce effective visualizations of the estimated causal effects and dose-response relationships. 

+ This code assumes you have K BKMR fits and that each of these fits were ran for the same number if MCMC iterations.

+ All effects are calculated as the average change in the outcome for a change in the exposure elements from a particular quantile to another quantile calculated across ALL imputed datasets. If there are no missing values in the Z matrix (in the mixture exposure), this is same contrast considered when only using the observed Z.  
+ All functions have the option to choose between an "approx" or "exact" method. The "exact" method combines the posterior samples from all MI fits and uses this posterior chain of length #iterations times #MI datasets for inference. The "approx" method uses the bkmr approx estimates and std errors from each MI fit and calculates an overall estimate and sd using Rubin's 1987 method. (When using the "exact" method, the functions take a while to run, so make sure you save the data frames to be used for plotting).

+ This code can also be used with only 1 BKMR fit. The additional flexibility with this code over what is included in the bkmr package is that you have the option to fix specified variables to a given quantile when creating overall risk and single variable risk plots. 
 
### g-BKMR




---------------
 
You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.
 

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
