---
title: "BKMRCMA Effect Of Joint Exposures when the Effect Modifier is Fixed"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BKMRCMA_Effectof_singleZ}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
 
```{r, include = FALSE}
knitr::opts_chunk$set(
  dpi = 300, 
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
```

```{r setup, results='hide', warning=FALSE, message=FALSE}
library(bkmr)
library(mixtools)
library(causalbkmr)
library(ggplot2)
library(ggpubr)
```

In this scenario, we have a continuous mediator $M$, a continuous outcome $Y$, and `x2` as the effect modifier on $Y$. The sample size is 50 and there are 3 covariates. 

We can generate a basic sample dataset analogous to the one presented in the QuickStart guide and proceed to fit the BKMR models in the same way. 
 
```{r , include = FALSE}
dat <-  cma_sampledata(N = 50, L=3, P=3, scenario=1, seed=7) 
head(dat$data, n = 3L)
dat = dat$data

A <- cbind(dat$z1, dat$z2, dat$z3)
X <- cbind(dat$x1, dat$x2, dat$x3)
y  <- dat$y
m  <- dat$M 

E.M <- NULL
E.Y <- dat$x2

Z.M <- cbind(A,E.M) 
Z.Y <- cbind(A, E.Y) 
Zm.Y <- cbind(Z.Y, m)

set.seed(1)
#fit.y <- kmbayes(y=y, Z=Zm.Y, X=X, iter=10000, verbose=TRUE, varsel=FALSE) 
#save(fit.y,file="bkmr_y.RData")

set.seed(2)
fit.y.TE <- kmbayes(y=y, Z=Z.Y, X=X, iter=10000, verbose=TRUE, varsel=FALSE) 
#save(fit.y.TE,file="bkmr_y_TE.RData")

set.seed(3)
#fit.m <- kmbayes(y=m, Z=Z.M, X=X, iter=10000, verbose=TRUE, varsel=FALSE) 
#save(fit.m,file="bkmr_m.RData")

X.predict <- matrix(colMeans(X),nrow=1)
sel<-seq(5000,10000,by=10)
```

 

### Joint effect of co-exposure to Z1, Z2 and Z3 and single variable effects, presented when the Effect Modifier is fixed at its 10th percentile or 90th percentile

```{r warning=FALSE, message=FALSE}
list.fit.y.TE <- list(fit.y.TE) 
colnames(list.fit.y.TE[[1]]$Z) <- c("z1", "z2", "z3", "E.Y")


overallrisks.y.TE.joint.x10 <- OverallRiskSummaries.MI(BKMRfits=list.fit.y.TE, qs = seq(0.1, 0.9, by = 0.05), q.fixed = 0.5, q.alwaysfixed = 0.1, index.alwaysfixed = 4, sel = sel, method="approx") 
 
overallrisks.y.TE.joint.x90 <- OverallRiskSummaries.MI(BKMRfits=list.fit.y.TE, qs = seq(0.1, 0.9, by = 0.05), q.fixed = 0.5, q.alwaysfixed = 0.9, index.alwaysfixed = 4, sel = sel, method="approx") 
 

pA <- ggplot(overallrisks.y.TE.joint.x10, aes(quantile, est, ymin = est - 1.96*sd, ymax = est + 1.96*sd)) +  geom_hline(yintercept=00, linetype="dashed", color="gray")+ 
  geom_pointrange()+ ggtitle("A")+ scale_y_continuous(name="estimate") + ylim(-1.3, 1.8)
 
pB <- ggplot(overallrisks.y.TE.joint.x90, aes(quantile, est, ymin = est - 1.96*sd, ymax = est + 1.96*sd)) +  geom_hline(yintercept=00, linetype="dashed", color="gray")+ 
  geom_pointrange()+ ggtitle("B")+ scale_y_continuous(name="estimate") + ylim(-1.3, 1.8)

ggarrange(pA , pB , ncol=2, nrow =1)
```

Interpretation of the point estimate in figures A, B:

$$E[Y^{z_1^*, z_2^*, z_3^*}|x_{EM} = x^q] - E[Y^{z_1, z_2, z_3}|x_{EM} = x^q]$$
Figure (A). Overall effect of the mixture (estimates and 95% credible interval) , by comparing the value of `h` when all of predictors are at a particular percentile as compared to when all of them are at their 50th percentile, while the effect modifier `E.Y` is fixed at it's 10th percentile;


Figure (B). Overall effect of the mixture (estimates and 95% credible interval) , by comparing the value of `h` when all of predictors are at a particular percentile as compared to when all of them are at their 50th percentile, while the effect modifier `E.Y` is fixed at it's 90th percentile. 



### Single exposure associations with outcome Y (estimates and 95% CI) presented when the age is fixed at its 10th percentile or 90th percentile


```{r}
singvarrisk.y.TE.joint.x10  <- SingVarRiskSummaries.MI(BKMRfits=list.fit.y.TE, which.z=c(1,2,3), qs.diff = c(0.25, 0.75), q.fixed = c(0.25, 0.50, 0.75), q.alwaysfixed = 0.1, index.alwaysfixed = 4, sel=sel, method = "approx")

singvarrisk.y.TE.joint.x90  <- SingVarRiskSummaries.MI(BKMRfits=list.fit.y.TE, which.z=c(1,2,3), qs.diff = c(0.25, 0.75), q.fixed = c(0.25, 0.50, 0.75), q.alwaysfixed = 0.9, index.alwaysfixed = 4, sel=sel, method = "approx")

pC <- ggplot(singvarrisk.y.TE.joint.x10 , aes(variable, est, ymin = est - 1.96*sd,  ymax = est + 1.96*sd, col = q.fixed)) +  geom_hline(aes(yintercept=0), linetype="dashed", color="gray")+ 
  geom_pointrange(position = position_dodge(width = 0.75)) +  coord_flip() + ggtitle("")+ theme(legend.position="none")+
  scale_x_discrete(name="")+ scale_y_continuous(name="estimate")  + ggtitle("C")

pD <- ggplot(singvarrisk.y.TE.joint.x90 , aes(variable, est, ymin = est - 1.96*sd,  ymax = est + 1.96*sd, col = q.fixed)) +  geom_hline(aes(yintercept=0), linetype="dashed", color="gray")+ 
  geom_pointrange(position = position_dodge(width = 0.75)) +  coord_flip() + ggtitle("")+ 
  scale_x_discrete(name="")+ scale_y_continuous(name="estimate")  + ggtitle("D") 

ggarrange(pC , pD , ncol=2, nrow =1)

```

Interpretation of the point estimate in figures C, D:

$Z_1$:

$$E[Y^{z_1^*, z_2^p, z_3^p}|x_{EM} = x^q] - E[Y^{z_1, z_2^p, z_3^p}|x_{EM} = x^q]$$
$Z_2$:

$$E[Y^{z_1^p, z_2^*, z_3^p}|x_{EM} = x^q] - E[Y^{z_1^p, z_2, z_3^p}|x_{EM} = x^q]$$
$Z_3$:

$$E[Y^{z_1^p, z_2^p, z_3^*}|x_{EM} = x^q] - E[Y^{z_1^p, z_2^p, z_3}|x_{EM} = x^q]$$


Figure (C). Single Exposure association (estimates and 95% credible intervals) while the effect modifier `E.Y` is fixed at it's 10th percentile. This plot compares the outcome when a single exposure is at the 75th vs. 25th percentile, when all the other exposures are fixed at either the 25th, 50th, or 75th percentile, and the effect modifier fixed at it's 10th percentile. 


Figure (D).  Single Exposure association (estimates and 95% credible intervals) while the effect modifier `E.Y` is fixed at it's 90th percentile. This plot compares the outcome when a single exposure is at the 75th vs. 25th percentile, and the effect modifier fixed at it's 10th percentile. 


### Functions for multiple Exposures are presented

In the follwing scenario, we have a continuous mediator $M$, a continuous outcome $Y$. `x1` and `x2` are both effect modifiers on $Y$. The sample size is 50 and there are 3 covariates. 

```{r}
dat <-  cma_sampledata(N = 50, L=3, P=3, scenario=5, seed=7) 
head(dat$data, n = 3L)
dat = dat$data

A <- cbind(dat$z1, dat$z2, dat$z3)
X <- cbind(dat$x1, dat$x2, dat$x3)
y  <- dat$y
m  <- dat$M 

E.M <- NULL
E.Y <- cbind(dat$x1, dat$x2)

Z.M <- cbind(A,E.M) 
Z.Y <- cbind(A, E.Y) 
Zm.Y <- cbind(Z.Y, m)

set.seed(2)
fit.y.TE <- kmbayes(y=y, Z=Z.Y, X=X, iter=10000, verbose=TRUE, varsel=FALSE) 
#save(fit.y.TE,file="bkmr_y_TE.RData")

X.predict <- matrix(colMeans(X),nrow=1)
sel<-seq(5000,10000,by=10)

list.fit.y.TE <- list(fit.y.TE)  
colnames(list.fit.y.TE[[1]]$Z) <- c("z1", "z2", "z3", "x1", "x2")
```

### Overall Risk Summaries for a list of fixed percentiles of the Effect modifiers
```{r}
ListofResTables <- OverallRiskSummaries.fixEY(BKMRfits=list.fit.y.TE, qs = seq(0.1, 0.9, by = 0.05), 
                           q.fixed = 0.5, q.alwaysfixed =  c(0.15, 0.85), 
                           EY.alwaysfixed.name =  c("x1", "x2"), sel = sel, method="approx")  

#ListofResTables[[1]]
#ListofResTables[[2]]

pE <- ggplot(ListofResTables[[1]], aes(quantile, est, ymin = est - 1.96*sd, ymax = est + 1.96*sd)) +  
  geom_hline(yintercept=00, linetype="dashed", color="gray")+ 
  geom_pointrange()+ ggtitle("E")+ scale_y_continuous(name="estimate", limits = c(-1, 1.5))  
pF <- ggplot(ListofResTables[[2]], aes(quantile, est, ymin = est - 1.96*sd, ymax = est + 1.96*sd)) +  
  geom_hline(yintercept=00, linetype="dashed", color="gray")+ 
  geom_pointrange()+ ggtitle("F")+ scale_y_continuous(name="estimate", limits = c(-1, 1.5)) 
ggarrange(pE , pF , ncol=2, nrow =1)
```

### Single Variable Risk Summaries for a list of fixed percentiles of the Effect modifiers

```{r}
ListofResTablesSingvar <- SingVarRiskSummaries.fixEY(list.fit.y.TE, which.z = c(1,2,3), qs.diff = c(0.25, 0.75), 
                                                     q.fixed = c(0.25, 0.50, 0.75), 
                                                     q.alwaysfixed = c(0.15, 0.85), z.names = c("z1", "z2", "z3"), 
                                                     EY.alwaysfixed.name =  c("x1", "x2"), sel = sel, method="approx") 
#ListofResTablesSingvar[[2]] 
#ListofResTablesSingvar[[2]]

pG <- ggplot(ListofResTablesSingvar[[1]] , aes(variable, est, ymin = est - 1.96*sd,  ymax = est + 1.96*sd, col = q.fixed)) +  
  geom_hline(aes(yintercept=0), linetype="dashed", color="gray")+ 
  geom_pointrange(position = position_dodge(width = 0.75)) +  coord_flip() + ggtitle("")+ 
  scale_x_discrete(name="")+ scale_y_continuous(name="estimate")  + ggtitle("G") 
pH <- ggplot(ListofResTablesSingvar[[2]] , aes(variable, est, ymin = est - 1.96*sd,  ymax = est + 1.96*sd, col = q.fixed)) +  
  geom_hline(aes(yintercept=0), linetype="dashed", color="gray")+ 
  geom_pointrange(position = position_dodge(width = 0.75)) +  coord_flip() + ggtitle("")+ 
  scale_x_discrete(name="")+ scale_y_continuous(name="estimate")  + ggtitle("H") 
ggarrange(pG , pH , ncol=2, nrow =1)
```


