---
title: "bkmrcma_example_scenario3"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bkmrcma_example_scenario3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
--- 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
```

```{r setup, results='hide', warning=FALSE, message=FALSE}
library(bkmr)
library(mixtools)
library(causalbkmr)
library(ggplot2)
```

## Sample simulated Dataset

Example with N=50, L=3 for *scenario 3* (continuous $Y$, binary $M$, no effect modification):

```{r warning=FALSE}
dat <-  cma_sampledata(N = 50, L=3, P=3, scenario=3, seed=7) 
head(dat$data, n = 3L)
dat = dat$data
```

## Fit BKMR Models

let $A$ be a $n$-by-$L$ matrix containing an exposure mixture comprised of $L$ elements,`E.M` and `E.Y` be effect modifiers of exposure-mediator and exposure-outcome relationship respectively, $y$, a vector of outcome data, and  $m$, a vector of mediator data.

`Z.M <- cbind(A,E.M)`

`Z.Y <- cbind(A,E.Y)`

Let `Z.M` be the exposures and effect modifers `E.M` and let `Z.Y` be the exposures and effect modifers `E.Y`, 
create one more matrix containing the exposures, effect modifier `Z.Y` and mediator,  precisely in that order.

`Zm.Y <- cbind(Z.Y,m)`

NOTE: the last column of the `Zm.Y` matrix *must* be your mediator in order for the functions to work properly.


```{r cache = TRUE, warning=FALSE, message = FALSE, results='hide'}
A <- cbind(dat$z1, dat$z2, dat$z3)
X <- cbind(dat$x1, dat$x2, dat$x3)
y  <- dat$y
m  <- dat$M 

E.M <- NULL
E.Y <- dat$x2

Z.M <- cbind(A,E.M) 
Z.Y <- cbind(A, E.Y) 
Zm.Y <- cbind(Z.Y, m)

set.seed(1)
fit.y <- kmbayes(y=y, Z=Zm.Y, X=X, iter=10000, verbose=TRUE, varsel=FALSE) 
#save(fit.y,file="bkmr_y.RData")

set.seed(2)
fit.y.TE <- kmbayes(y=y, Z=Z.Y, X=X, iter=10000, verbose=TRUE, varsel=FALSE) 
#save(fit.y.TE,file="bkmr_y_TE.RData")

set.seed(3)
fit.m <- kmbayes(y=m, Z=Z.M, X=X, iter=10000, verbose=TRUE, varsel=FALSE) 
#save(fit.m,file="bkmr_m.RData")
```


## Values at which to predict counterfactuals

Mean level of confounders:
```{r }
X.predict <- matrix(colMeans(X),nrow=1)
``` 

We define the change in exposure for which you want to estimate the mediation effects: in this example, we will consider a change in all exposures from their 25th to 75th percentiles, fixing age (`E.Y`) at testing to its 10th and 90th percentiles. However, this contrast can be anything. 

Note: If modifiers are considered, you should fix the levels of the modifiers

```{r contrasts, warning=FALSE}
astar <- c(apply(A, 2, quantile, probs=0.25))  
a <- c(apply(A, 2, quantile, probs=0.75))

e.y10 = quantile(E.Y, probs=0.1)
e.y90 = quantile(E.Y, probs=0.9)
```
The index of the MCMC iterations to be used for inference:

```{r}
sel<-seq(5000,10000,by=10)
```

## Estimate TE for BKMR

Estimate the TE for a change in the exposures from $a^*$ to $a$ fixing Effect modifier at testing to its 10th percentile or 90th percentile:

```{r TE, warning=FALSE}
e.y10 = quantile(E.Y, probs=0.1)
e.y90 = quantile(E.Y, probs=0.9)

TE.ey10 <- TE.bkmr(a=a, astar=astar, e.y = e.y10, fit.y.TE=fit.y.TE, X.predict=X.predict, alpha=0.05, sel=sel, seed=122)

TE.ey90 <- TE.bkmr(a=a, astar=astar, e.y = e.y90, fit.y.TE=fit.y.TE, X.predict=X.predict, alpha=0.05, sel=sel, seed=122)
```


Look at the posterior mean, median, and 95% CI for TE:

```{r}
TE.ey10$est
TE.ey90$est

plotdf <- as.data.frame(TE.ey10$est)
plotdf["Effect"] <- rownames(plotdf)
ggplot(plotdf, aes(Effect, mean, ymin = lower, ymax = upper))  + 
  geom_pointrange(position = position_dodge(width = 0.75))  +  coord_flip()
```



## Estimate CDE for BKMR

Estimate the CDE for a change in the exposures from $a^*$ to $a$, fixing the mediator at its 10th, 50th, and 75th percentile and the effect modifier at testing at its 10th percentile:

```{r CDE, warning=FALSE} 
CDE.ey10 <- CDE.bkmr(a=a, astar=astar, e.y = e.y10, m.quant=c(0.1,0.5,0.75), fit.y=fit.y, alpha=0.05, sel=sel, seed=777)

CDE.ey90 <- CDE.bkmr(a=a, astar=astar, e.y = e.y90, m.quant=c(0.1,0.5,0.75), fit.y=fit.y, alpha=0.05, sel=sel, seed=777)
```

Look at the posterior mean, median, and 95% CI for the CDEs:



```{r warning=FALSE} 
CDE.ey10$est
CDE.ey90$est
```

Plotting:

```{r warning=FALSE} 
plotdf <- as.data.frame(CDE.ey10$est)
plotdf["Effect"] <- rownames(plotdf)
ggplot(plotdf, aes(Effect, mean, ymin = lower, ymax = upper ))  + 
  geom_pointrange(position = position_dodge(width = 0.75))  +  coord_flip()
```



## Estimate NDE/NIE for BKMR   

Estimate the TE, NDE and NIE for a change in the exposures from $a^*$ to $a$ fixing age at testing to its 90th percentile.
 
Note: this step takes a while to run and will take longer for more complex BKMR fits, longer `sel` vectors and larger.

```{r NDENIE, warning=FALSE, message=FALSE, results='hide'}
mediationeffects.ey10  <- mediation.bkmr(a=a, astar=astar, e.y = e.y10, fit.m=fit.m, fit.y=fit.y, fit.y.TE=fit.y.TE, X.predict.M=X.predict, X.predict.Y=X.predict, alpha=0.05, sel=sel, seed=22, K=10)

mediationeffects.ey90  <- mediation.bkmr(a=a, astar=astar, e.y = e.y90, fit.m=fit.m, fit.y=fit.y, fit.y.TE=fit.y.TE, X.predict.M=X.predict, X.predict.Y=X.predict, alpha=0.05, sel=sel, seed=22, K=10) 
```
 
Look at the posterior mean, median, and 95% CI for the TE, NDE, and NIE

```{r}
mediationeffects.ey10$est
mediationeffects.ey90$est
```

Plotting

```{r}
plotdf <- as.data.frame(mediationeffects.ey10$est)
plotdf["Effect"] <- rownames(plotdf)
ggplot(plotdf, aes(Effect, mean, ymin = lower, ymax = upper ))  + 
  geom_pointrange(position = position_dodge(width = 0.75))  +  coord_flip()
```

## Summary statistics of the predictor-response function

### Risk Summary For Totel Effect

```{r TERisk, warning=FALSE}
riskSummary10 = TERiskSummaries.CMA(fit.TE = fit.y.TE, e.y=e.y10, e.y.name = "E.Y", sel=sel)

ggplot(riskSummary10,
       aes(quantile,
           est,
           ymin = est - 1.96 * sd,
           ymax = est + 1.96 * sd)) +
  geom_pointrange()

riskSummary90 = TERiskSummaries.CMA(fit.TE = fit.y.TE, e.y=e.y90, e.y.name = "E.Y", sel=sel)

ggplot(riskSummary90,
       aes(quantile,
           est,
           ymin = est - 1.96 * sd,
           ymax = est + 1.96 * sd)) +
  geom_pointrange()
```


### Risk Summary For Controlled Direct Effect

```{r CDERisk, warning=FALSE, message=FALSE, results='hide'} 
# CDE 
CDEriskSummary10 = CDERiskSummaries.CMA(fit.y = fit.y, e.y = e.y10, e.y.name = "E.Y", m.name = "m", sel = sel)

```

```{r}
ggplot(CDEriskSummary10, aes(quantile, est, ymin = est - 1.96*sd, 
                             ymax = est + 1.96*sd, col = m)) + 
  geom_pointrange(position = position_dodge(width = 0.75))
```

```{r CDErisk90, warning=FALSE, message=FALSE, results='hide'} 
CDEriskSummary90 = CDERiskSummaries.CMA(fit.y = fit.y, e.y = e.y90, e.y.name = "E.Y", m.name = "m", sel = sel)
```

```{r}
ggplot(CDEriskSummary90, aes(quantile, est, ymin = est - 1.96*sd, 
                             ymax = est + 1.96*sd, col = m)) + 
  geom_pointrange(position = position_dodge(width = 0.75))
```

## Single-predictor health risks

### Total Effect
```{r warning=FALSE, message=FALSE}
 
risks.singvar10 = SingVarRiskSummaries.CMA(BKMRfits = fit.y.TE, which.z = 1:3,
                                           e.y=e.y10, e.y.names="E.Y",
                                           sel=sel)
ggplot(risks.singvar10, aes(variable, est, ymin = est - 1.96*sd,
                            ymax = est + 1.96*sd, col = q.fixed)) +
  geom_pointrange(position = position_dodge(width = 0.75)) +
  coord_flip()


risks.singvar90 = SingVarRiskSummaries.CMA(BKMRfits = fit.y.TE, which.z = 1:3,
                                           e.y=e.y90, e.y.names="E.Y",
                                           sel=sel)
ggplot(risks.singvar90, aes(variable, est, ymin = est - 1.96*sd,
                            ymax = est + 1.96*sd, col = q.fixed)) +
  geom_pointrange(position = position_dodge(width = 0.75)) +
  coord_flip()
```


### Controlled Direct Effect 

```{r CDERisksingvar10, warning=FALSE, message=FALSE, results='hide'} 
# single variable controlled direct effects
CDErisks.singvar10 = CDESingVarRiskSummaries.CMA(BKMRfits = fit.y,
                                           e.y=e.y10, e.y.names="E.Y", m.name = "m",
                                           sel=sel)
```


```{r}
ggplot(CDErisks.singvar10, aes(variable, est, ymin = est - 1.96*sd,
                            ymax = est + 1.96*sd, col = q.fixed, linetype = m.fixed)) +
  geom_pointrange(position = position_dodge(width = 0.75)) +
  coord_flip()
```

```{r CDERisksingvaar, warning=FALSE, message=FALSE, results='hide'} 
CDErisks.singvar90 = CDESingVarRiskSummaries.CMA(BKMRfits = fit.y,
                                                 e.y=e.y90, e.y.names="E.Y", m.name = "m",
                                                 sel=sel)
```

```{r}
ggplot(CDErisks.singvar90, aes(variable, est, ymin = est - 1.96*sd,
                               ymax = est + 1.96*sd, col = q.fixed, linetype = m.fixed)) +
  geom_pointrange(position = position_dodge(width = 0.75)) +
  coord_flip()

```
