---
title: "BKMRCMA Effect Of Joint Exposures when the Effect Modifier is Fixed"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BKMRCMA_Effectof_singleZ}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
 
```{r, include = FALSE}
knitr::opts_chunk$set(
  dpi = 300, 
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
```

```{r setup, results='hide', warning=FALSE, message=FALSE}
library(bkmr)
library(mixtools)
library(causalbkmr)
library(ggplot2)
library(ggpubr)
```

In this scenario, we have a continuous mediator $M$, a continuous outcome $Y$, and `x2` as the effect modifier on $Y$. The sample size is 50 and there are 3 covariates. 

We can generate a basic sample dataset analogous to the one presented in the QuickStart guide and proceed to fit the BKMR models in the same way. 
 
```{r , include = FALSE}
dat <-  cma_sampledata(N = 50, L=3, P=3, scenario=1, seed=7) 
head(dat$data, n = 3L)
dat = dat$data

A <- cbind(dat$z1, dat$z2, dat$z3)
X <- cbind(dat$x1, dat$x2, dat$x3)
y  <- dat$y
m  <- dat$M 

E.M <- NULL
E.Y <- dat$x2

Z.M <- cbind(A,E.M) 
Z.Y <- cbind(A, E.Y) 
Zm.Y <- cbind(Z.Y, m)

set.seed(1)
#fit.y <- kmbayes(y=y, Z=Zm.Y, X=X, iter=10000, verbose=TRUE, varsel=FALSE) 
#save(fit.y,file="bkmr_y.RData")

set.seed(2)
fit.y.TE <- kmbayes(y=y, Z=Z.Y, X=X, iter=10000, verbose=TRUE, varsel=FALSE) 
#save(fit.y.TE,file="bkmr_y_TE.RData")

set.seed(3)
#fit.m <- kmbayes(y=m, Z=Z.M, X=X, iter=10000, verbose=TRUE, varsel=FALSE) 
#save(fit.m,file="bkmr_m.RData")

X.predict <- matrix(colMeans(X),nrow=1)
sel<-seq(5000,10000,by=10)
```



```{r TEModels, warning=FALSE}
astar <- c(apply(A, 2, quantile, probs=0.25))  
a <- c(apply(A, 2, quantile, probs=0.75))

e.y10 = quantile(E.Y, probs=0.1)
e.y90 = quantile(E.Y, probs=0.9)

TE.ey10 <- TE.bkmr(a=a, astar=astar, e.y = e.y10, fit.y.TE=fit.y.TE, X.predict=X.predict, alpha=0.05, sel=sel, seed=122)

TE.ey90 <- TE.bkmr(a=a, astar=astar, e.y = e.y90, fit.y.TE=fit.y.TE, X.predict=X.predict, alpha=0.05, sel=sel, seed=122)
```


### Joint effect of co-exposure to Z1, Z2 and Z3 and single variable effects, presented when the Effect Modifier is fixed at its 10th percentile or 90th percentile

```{r warning=FALSE, message=FALSE}
list.fit.y.TE <- list(fit.y.TE) 
colnames(list.fit.y.TE[[1]]$Z) <- c("z1", "z2", "z3", "E.Y")


overallrisks.y.TE.joint.x10 <- OverallRiskSummaries.MI(BKMRfits=list.fit.y.TE, qs = seq(0.1, 0.9, by = 0.05), q.fixed = 0.5, q.alwaysfixed = 0.1, index.alwaysfixed = 4, sel = sel, method="approx") 
 
overallrisks.y.TE.joint.x90 <- OverallRiskSummaries.MI(BKMRfits=list.fit.y.TE, qs = seq(0.1, 0.9, by = 0.05), q.fixed = 0.5, q.alwaysfixed = 0.9, index.alwaysfixed = 4, sel = sel, method="approx") 
 

pA <- ggplot(overallrisks.y.TE.joint.x10, aes(quantile, est, ymin = est - 1.96*sd, ymax = est + 1.96*sd)) +  geom_hline(yintercept=00, linetype="dashed", color="gray")+ 
  geom_pointrange()+ ggtitle("")+ scale_y_continuous(name="estimate") 
 
pC <- ggplot(overallrisks.y.TE.joint.x90, aes(quantile, est, ymin = est - 1.96*sd, ymax = est + 1.96*sd)) +  geom_hline(yintercept=00, linetype="dashed", color="gray")+ 
  geom_pointrange()+ ggtitle("")+ scale_y_continuous(name="estimate") 

ggarrange(pA , pC , ncol=2, nrow =1)
```


### Single exposure associations with outcome Y (estimates and 95% CI) presented when the age is fixed at its 10th percentile or 90th percentile


```{r}
singvarrisk.y.TE.joint.x10  <- SingVarRiskSummaries.MI(BKMRfits=list.fit.y.TE, which.z=c(1,2,3), qs.diff = c(0.25, 0.75), q.alwaysfixed = 0.1, index.alwaysfixed = 4, sel=sel, method = "approx")

singvarrisk.y.TE.joint.x90  <- SingVarRiskSummaries.MI(BKMRfits=list.fit.y.TE, which.z=c(1,2,3), qs.diff = c(0.25, 0.75),q.fixed = c(0.25, 0.50, 0.75), q.alwaysfixed = 0.9, index.alwaysfixed = 4, sel=sel, method = "approx")

pB <- ggplot(singvarrisk.y.TE.joint.x10 , aes(variable, est, ymin = est - 1.96*sd,  ymax = est + 1.96*sd, col = q.fixed)) +  geom_hline(aes(yintercept=0), linetype="dashed", color="gray")+ 
  geom_pointrange(position = position_dodge(width = 0.75)) +  coord_flip() + ggtitle("")+ theme(legend.position="none")+
  scale_x_discrete(name="")+ scale_y_continuous(name="estimate")  

pD <- ggplot(singvarrisk.y.TE.joint.x90 , aes(variable, est, ymin = est - 1.96*sd,  ymax = est + 1.96*sd, col = q.fixed)) +  geom_hline(aes(yintercept=0), linetype="dashed", color="gray")+ 
  geom_pointrange(position = position_dodge(width = 0.75)) +  coord_flip() + ggtitle("")+ theme(legend.position="none")+
  scale_x_discrete(name="")+ scale_y_continuous(name="estimate")  

ggarrange(pB , pD , ncol=2, nrow =1)

```


Interpretation of the point estimate in figures A, C:

$$E[Y^{z_1^*, z_2^*, z_3^*}|x_{EM} = x_q] - E[Y^{z_1, z_2, z_3}|x_{EM} = x_q]$$

Interpretation of the point estimate in figures B, D:


$$E[Y^{z_1^*, z_2, z_3}|x_{EM} = x_q] - E[Y^{z_1, z_2, z_3}|x_{EM} = x_q]$$

$$E[Y^{z_1, z_2^*, z_3}|x_{EM} = x_q] - E[Y^{z_1, z_2, z_3}|x_{EM} = x_q]$$
$$E[Y^{z_1, z_2, z_3^*}|x_{EM} = x_q] - E[Y^{z_1, z_2, z_3}|x_{EM} = x_q]$$
