---
title: "MI BKMR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MI_BKMR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
```

```{r setup, results='hide', warning=FALSE, message=FALSE}
library(bkmr)
library(causalbkmr)
library(ggplot2) 
library(magrittr)
data("BKMRfits10")
```

## Overall Risk

If the models were fit for 10,000 iterations this would be:

```{r}
sel.MI <- seq(5001,10000, by = 5) 
```

Fit new `OverallRiskSummaries` function with our MI BKMR fits using approx method:


```{r cache=TRUE, message=FALSE, warning=FALSE, results='hide'}
overallrisks.MI <- OverallRiskSummaries.MI(BKMRfits = BKMRfits10, qs = seq(0.1, 0.9, by = 0.05), 
                                           q.fixed = 0.5, sel = sel.MI, method = "approx") 
```

Rerun the `OverallRiskSummaries` function but now FIXING the quantile for z2 to 0.25 (for all comparisons)


NOTE: you can fix one or more elements of the mixture, but the quantile you are fixing them to needs to be the same (q.alwaysfixed)

```{r  cache=TRUE, message=FALSE, warning=FALSE, results='hide'}
overallrisks.MI.fixed <- OverallRiskSummaries.MI(BKMRfits = BKMRfits10, qs = seq(0.1, 0.9, by = 0.05), 
                             q.fixed = 0.75, q.alwaysfixed = 0.25, 
                             index.alwaysfixed = 2, sel = sel.MI, method="approx") 
```


You can now plot this data frame as you normally would for a BKMR fit:

```{r  fig.fullwidth=TRUE}
ggplot(overallrisks.MI, aes(quantile, est, ymin = est - 1.96 * sd, ymax = est + 1.96 * sd)) +  
  geom_hline(yintercept = 00, linetype = "dashed", colo = "gray") + 
  geom_pointrange()+ ggtitle("") + scale_y_continuous(name="estimate")
```

Plot for the case where you fixed the quantile of 1 (or more) mixture elements.

If you are making multiple of these plots for different quantiles, you will most likely want to fix the y limits so that the plots are directly comparable.

```{r  fig.fullwidth=TRUE}
ggplot(overallrisks.MI.fixed, aes(quantile, est, ymin = est - 1.96*sd, ymax = est + 1.96*sd)) +
  geom_hline(yintercept=00, linetype="dashed", color="gray") + 
  geom_pointrange()+ ggtitle("")+ scale_y_continuous(name="estimate")
```

##   Single Variable Risk Generation and Plot 
 
Fit new `SingVarRiskSummaries` function with our MI BKMR fits:

```{r cache=TRUE, message=FALSE, warning=FALSE}  
singvarrisk.MI <- SingVarRiskSummaries.MI(BKMRfits=BKMRfits10, qs.diff = c(0.25, 0.75),
                         q.fixed = c(0.25, 0.50, 0.75), sel=sel.MI, method = "approx")
```

Rerun the `SingVarRiskSummaries.MI` function but now *fixing* the quantile for `z2` to 0.25 (for all comparisons)

NOTE: you can fix one or more elements of the mixture, but the quantile you are fixing them to needs to be the same (`q.alwaysfixed`).

Also, you need to specify which.z to NOT include the fixed elements (it will still run if you dont do this, but your plot will look funny).

```{r cache=TRUE, message=FALSE, warning=FALSE, fig.fullwidth=TRUE}  
singvarrisk.MI.fixed <- SingVarRiskSummaries.MI(BKMRfits = BKMRfits10, which.z=c(1,3,4), 
                               qs.diff = c(0.25, 0.75),  q.fixed = c(0.25, 0.50, 0.75), 
                               q.alwaysfixed = 0.25, index.alwaysfixed = 2, 
                               sel=sel.MI, method = "approx")
 
## plot the single variable dataframe for the MI fits
ggplot(singvarrisk.MI, aes(variable, est, ymin = est - 1.96*sd,  
                           ymax = est + 1.96*sd, col = q.fixed)) +  
  geom_hline(aes(yintercept=0), linetype="dashed", color="gray") + 
  geom_pointrange(position = position_dodge(width = 0.75)) +  
  coord_flip() + ggtitle("")+ 
  scale_x_discrete(name="Variable")+ scale_y_continuous(name="estimate")
```

Plot for the case where you fixed the quantile of 1 (or more) mixture elements 

NOTE: if you do not change `which.z` to NOT include the fixed element, then the graph will have undesired points.

```{r r, fig.fullwidth=TRUE}
ggplot(singvarrisk.MI.fixed, aes(variable, est, ymin = est - 1.96*sd,  
                                 ymax = est + 1.96*sd, col = q.fixed)) +  
  geom_hline(aes(yintercept=0), linetype="dashed", color="gray") + 
  geom_pointrange(position = position_dodge(width = 0.75)) +  coord_flip() + ggtitle("")+ 
  scale_x_discrete(name="Variable")+ scale_y_continuous(name="estimate")
```

## Univariate Risk Generation and Plot 

Fit new `PredictorResponseUnivar` function for our MI fits.

This part can easily be run in parallel by only selecting one `z` at a time (`which.z=1`) and then rbinding the dataframes.

```{r cache=TRUE, message=FALSE, warning=FALSE} 
univar.MI <- PredictorResponseUnivar.MI(BKMRfits10, ngrid = 50, q.fixed = 0.5, 
                                        sel = sel.MI, method="approx") 
```

Plot univariate response functions:

```{r g, fig.fullwidth=TRUE}
ggplot(univar.MI, aes(z, est, ymin = est - 1.96*se, ymax = est + 1.96*se)) + 
  geom_smooth(stat = "identity") + ylab("h(z)") + facet_wrap(~ variable)+ggtitle("")
```

##  Bivariate Risk Generation and Plot  

First fit the new `PredictorResponseBivar` function to our MI fits using the approx method:

```{r cache=TRUE, message=FALSE, warning=FALSE}  
bivar.MI <- PredictorResponseBivar.MI(BKMRfits = BKMRfits10,  
                                      min.plot.dist = 1, sel=seq(5001,10000,by=500), 
                                      method="approx")  
```

 Now, apply the UNEDITED function `PredictorResponseBivarLevels` using the Z matrix containing ALL observations from the K MI datasets:

```{r cache=TRUE, message=FALSE, warning=FALSE}  
Z.MI <- Z.complete.MI(BKMRfits10)
bivar.levels.MI <- PredictorResponseBivarLevels(pred.resp.df = bivar.MI, 
                                                Z=Z.MI, both_pairs = TRUE, 
                                                qs = c(0.25, 0.5, 0.75))
```

Create the plot for the bivariate curves:

```{r plot, fig.fullwidth=TRUE}
ggplot(bivar.levels.MI, aes(z1, est)) + geom_smooth(aes(col = quantile), stat = "identity") + 
  facet_grid(variable2 ~ variable1) + ggtitle("h(expos1 | quantiles of expos2)") + xlab("expos1")
```
 
